\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\date{}

\begin{document}

\hypertarget{spooky-action-at-a-distance}{%
\section{Spooky Action at a
Distance}\label{spooky-action-at-a-distance}}

Some text here. I wonder if this is OK.

It is of course much slower than the lightning fast tup.

\hypertarget{advantages}{%
\subsection{Advantages}\label{advantages}}

\begin{itemize}
\tightlist
\item
  Easily configured.
\item
  Look I cite @lion2010.
\item
  That means I am awesome.
\end{itemize}

New check. This ought to update.

Now this works via \href{http://prose.io}{prose.io} which is good for
images.

\href{https://stackedit.io}{Stackedit} has math rendering so that's a
huge plus.

Plus I know math.

Honest!

\[\int_0^\infty\sin{x} = ?\]

\(\prec\) stands for accessibility. Basically the order relation.

\href{https://dillinger.io/}{Dillinger} has great rendering for math,
but no images and it doesn't understand single dollar symbols for math.

Well so what.

That's sort of math as well. Look it up. dgd I do TeX too

\textbf{Bye.}

Hahaha

\hypertarget{references}{%
\section{References}\label{references}}

\end{document}
